Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-06-10 03_Prep_data.Rmd
simplification and corrections

# Calculate AUDPC using final severity and first sign of disease - 7 days
source("R/AUDPC_for_single_obs.R") 
```

@@

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole",
          row_spacing == 0.75) %>%
   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
   summarise(DMI_trts = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   kable(caption = "Number of treatments for each trial and the error type reported") %>%
   kable_styling(fixed_thead = T) %>% 
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

@@

   clusters[i, "n"] <-
      nrow(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i, "cluster_1"] &
                          slim_PM_dat$cluster_2 == clusters[i, "cluster_2"] &
                          slim_PM_dat$cluster_3 == clusters[i, "cluster_3"],])

   clusters[i, "n_x_trial"] <-
      length(unique(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i, "cluster_1"] &
                                   slim_PM_dat$cluster_2 == clusters[i, "cluster_2"] &
                                   slim_PM_dat$cluster_3 == clusters[i, "cluster_3"],
                                "trial_ref"]))

>>>>

source("R/AUDPC_for_single_obs.R") # Calculate AUDPC using final severity and first sign of disease - 7 days
source("R/same.R") # matches each element of a vector and does not return NAs
```

@@

```{r variance_types}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
   summarise(DMI_trts = length(Y_error_type)) %>%
   arrange(Y_error_type) %>%
   kable(caption = "Number of treatments for each trial and the error type reported") %>%
   #kable_styling(fixed_thead = T) %>% 
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

@@

   clusters[i, "n"] <-
      nrow(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
                          same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
                          same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),])

   clusters[i, "n_x_trial"] <-
      length(unique(slim_PM_dat[same(slim_PM_dat$cluster_1, clusters[i, "cluster_1"]) &
                                   same(slim_PM_dat$cluster_2, clusters[i, "cluster_2"]) &
                                   same(slim_PM_dat$cluster_3, clusters[i, "cluster_3"]),
                                "trial_ref"]))
